New lower bounds for Schur and weak Schur numbers

### 2021-05-01 article/weakschur.tex
rien
quelques typo

Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a))\]
\end{definition}

@@

if \(x+\pi(y)\geqslant a\):
\begin{align*}
 \pi(x+y) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)\\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
& = x+\pi(y)
\end{align*}
\end{proof}

@@

\begin{proof}[\textsc{Proof.}]
Let \((x,y)\in (\mathbb{N}^*)^2\),

\begin{align*}
 \pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
& =(Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
& =\pi(x+y)
\end{align*}
\end{proof}

@@

In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.

@@

if \(x \mod a \leqslant b\):
\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+\text{x mod a}+a=x\)
\end{proof}

@@

\begin{itemize}
\item if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
\item if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\item if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
\end{itemize}

>>>>

Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
\end{definition}

@@

if \(x+\pi(y)\geqslant a\):
\begin{align*}
 \pi(x+y) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)\\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) \\
& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
& = x+\pi(y)
\end{align*}
\end{proof}

@@

\begin{proof}[\textsc{Proof.}]
Let \((x,y)\in (\mathbb{N}^*)^2\),
\begin{align*}
 \pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\mod a) \\
& = (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
& =(Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
& =\pi(x+y)
\end{align*}
\end{proof}

@@

In the following theorem, \(\lambda\) is the function which maps an element \(x\) to its line number as mentioned in the intuitive explanation.

@@

if \(x \mod a \leqslant b\):
\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+(x \mod a)+a=x\)
\end{proof}

@@

\begin{itemize}
\item if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
\item if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n (\text{ we will note } x \in \mathcal{C}): f(x)=g(\pi(x))\)
\item if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n (\text{ we will note } x \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
\end{itemize}
